A Semantic Proof of Generalised Cut Elimination for Deep Inference

### 2025-05-02 journal-version/sections/introduction.tex
[ tex ] speculative list of improvements to this version

>>>>

\subsection{Differences from the MFPS version}

\bob{This is a wishlist for now...}

\begin{enumerate}
\item We present Systems BV, MAV, NEL, MAUV, and MAUVE in full in \autoref{sec:mav-syntax}.
\item We include several examples of the use of the systems, in \autoref{sec:mav-examples}, including its use in establishing simulation results, and the similarity with Concurrent Kleene Algebras.
\item We include more explanation of why Okada's Phase Space semantic approach does not work for BV and its extensions.
\item We explicitly define the semantics of each of the systems we consider in \autoref{sec:mav-semantics}.
\item We explore the consequences of completeness more thoroughly \bob{What?}
\item We add the Kleene star to the systems explored.
\item Links to the Agda formalisation are now inline, instead of being in the appendix.
\end{enumerate}
